A User-Extensible and Adaptable Parser Architecture

### 2008-12-08 doc/sgai-2008-slides.tex
Some improvements.

        \item [Currently] Most commonly used anti-spam techniques are
            content-based, and require each mail to be accepted before
            determining its spam status.

@@

        \item [Conclusion] This method requires a parser for Postfix log
            files.

@@

\section{Input Characteristics}

\begin{frame}{Input Characteristics}

@@

    Sample log line: \texttt{NOQUEUE\@: reject: RCPT from
    client.example.net[192.0.2.1]: 554 5.7.1 <alice@example.net>: Relay
    access denied; from=<eve@example.com> to=<alice@example.net> proto=SMTP
    helo=<client.example.com>}

@@

\section{Architecture}

\begin{frame}{Architecture}

@@

    The architecture is divided into three parts:

@@

        \item [Actions] Each action performs the processing required, e.g.\
            create a new data structure when a client connects; record than
            an anti-spam measure was successful; commit the data structure
            when all processing is complete.

        \item [Rules] Each rule matches one type of log line, e.g.\ the log
            line resulting from client connecting, a mail successfully
            delivered, or a mail rejected by an anti-spam measure.

@@

\section{Features of the Architecture}

\begin{frame}{Features of the Architecture}

@@

        \item The architecture is capable of parsing inputs that are not
            completely understood, e.g.\ when developing a parser: the
            framework will warn about unparsed inputs but will continue on
            parsing as best it can.  \timingnote{Emphasise this.}

        \item Rules can be tagged with conditions which must hold before
            the rule will be used to match an input.

@@

        \item Rules can be changed or added by actions while the parser is
            running, allowing dynamically changing parsing, e.g.\ macros.
            This feature must be used with care.  \timingnote{Currying
            functions in a calculator might be a good example.}

@@

\section{Results}

\begin{frame}{Results}

@@

        \item 169 rules parsing 522 contiguous log files: the top 10\% of
            the rules match 85.03\% of the log lines, the remainder tailing
            off similar to a Power Law distribution.

        \item Most actions are triggered by only one or two rules.

        \item The top three actions are triggered by 41, 49, and 59 rules.
            \timingnote{build/stats-action-distribution}
            \timingnote{uninteresting, save\_data, delivery\_rejected}

        \item XXX MORE\@?

@@

\section{Efficiency}

\begin{frame}{Efficiency}

@@

        \item Median throughput is 80.85~MB (480,569 log lines) parsed per
            minute.

@@

        \item Rules are sorted by how frequently they match, resulting in a
            mean reduction of 14.78\% in parsing time compared to using
            unsorted rules.

@@

        \item Parsing time scales linearly with input size, but
            \textit{is\/} affected by input content.

@@

        \item Easy to develop a flexible yet strict parser.

        \item Easy for users to parse new or changed inputs.

>>>>

        \item [Currently] Most of the commonly used anti-spam techniques
            are content-based, and require each mail to be accepted before
            determining its spam status.

@@

        \item [Therefore] This method requires a parser for Postfix log
            files.

@@

\section{Characteristics Of The Input: Postfix Log Files}

\begin{frame}{Characteristics Of The Input: Postfix Log Files}

@@

@@

\section{Parser Architecture}

\begin{frame}{Parser Architecture}

@@

    The parser architecture is divided into three parts: Framework,
    Actions, and Rules.

@@

        \item [Actions] Each action performs the processing required by one
            type of log line.  Actions correspond to events: events within
            Postfix create log lines, and actions perform the processing
            required by those events.

        \item [Rules] Each rule matches one log line variant, e.g.\ the log
            line resulting from client connecting, a mail successfully
            delivered, or a mail rejected by an anti-spam measure.

@@

\section{Features Of The Architecture}

\begin{frame}{Features Of The Architecture}

@@

        \item The architecture can be used when parsing input files that
            are not completely understood or that do not have 100\% parsing
            coverage.  \timingnote{Emphasise this.}

        \item Rules can be tagged with conditions which must hold before
            the rule will be used when attempting to match an input.

@@

        \item Rules can be added, changed, or removed by actions while the
            parser is running, allowing dynamically changing parsing, e.g.\
            macros.  This feature must be used with care.
            \timingnote{Currying functions in a calculator might be a good
            example.}

@@

\section{Results Of Writing A Parser Using This Architecture}

\begin{frame}{Results Of Writing A Parser Using This Architecture}

@@

        \item Zero false positives or false negatives.

        \item 169 rules parsing 522 contiguous log files: the top 10 rules
            match 85.03\% of the log lines, the remainder tail off similar
            to a Power Law distribution.

        \item 18 actions; most are triggered by only one or two rules.
            \timingnote{client connecting, postfix reloading}

        \item The top three actions are triggered by 41, 49, and 59 rules.
            \timingnote{build/stats-action-distribution:}
            \timingnote{uninteresting, save\_data, delivery\_rejected}

@@

\section{Parser Efficiency}

\begin{frame}{Parser Efficiency}

@@

        \item Median throughput is 80.85~MB (480,569 log lines) parsed per
            minute; median log file size is 50 MB, containing 285,000 log
            lines.

@@

        \item Rules are sorted by how frequently they match, resulting in a
            mean reduction of 14.78\% in parsing time compared to using
            unsorted rules.  Priority attribute can be used to override
            this.

@@

        \item Parsing time scales linearly with input size, but
            \textit{is\/} affected by input content: the content determines
            the actions that will run, and some actions take longer to run
            than others.

@@

        \item Parser Architecture makes it easy to develop a flexible yet
            strict parser.

        \item Parser Architecture makes it easy for users to parse new or
            changed inputs.
